D3064R0: How to Avoid OOTA Without Really Trying

### 2024-04-05 ootavacuous.tex
Fix typo
This typo has been around for a long time and I noticed it on several
occasions, but I haven't gotten around to fixing it until now.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>
Make myself the first author
This takes up Paul's generous offer to give first authorship to me.  It
also removes TBD (who doesn't seem to have contributed anything yet) and
changes the paper's date from February to April.

Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

\author{
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}} \and
The Indefatigible TBD
}
\date{Feburary 16, 2024 (Post-Pre-Tokyo)}
\maketitle{}

@@

In contrast, consider
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1},
which differs from
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
only in the initial values (1 instead of 0) and the \co{exists}
clause (0 instead of 1).
Note that an execution satisfying the updated \co{exists} clause is again
a OOTA cycle.

>>>>

\author{
Alan Stern\\{\small \email{stern@rowland.harvard.edu}} \and
Paul E.~McKenney\\{\small \email{paulmck@kernel.org}} \and
Michael Wong\\{\small \email{fraggamuffin@gmail.com}} \and
Maged Michael\\{\small \email{maged.michael@gmail.com}}
}
\date{April 5, 2024 (Post-Pre-Tokyo)}
\maketitle{}

@@

In contrast, consider
Listing~\ref{lst:OOTA Multiplication Example, Initial Value 1},
which differs from
Listing~\ref{lst:OOTA Multiplication Example, Initial Value Zero}
only in the initial values (1 instead of 0) and the \co{exists}
clause (0 instead of 1).
Note that an execution satisfying the updated \co{exists} clause is again
an OOTA cycle.
